Computing Entropies With Nested Sampling

### 2017-07-09 paper/ms.tex
Pareto section

\subsection{Computational cost}

>>>>

\section{Example 3: Data with Pareto distribution}

Consider a situation where the probability distribution for some data values
$\x = \{x_1, x_2, ..., x_n\}$ is a Pareto distribution, conditional on
a minimum value $x_{\rm min}=1$ and a slope $\alpha$:
\begin{align}
p(\x | \alpha) &= \prod_{i=1}^n \frac{1}{x_i^{\alpha + 1}}
\end{align}
where all of the $x_i$ are greater than $x_{\rm min} = 1$.
If $\alpha$ is relatively low (close to zero) then this distribution is
very heavy-tailed, and as $\alpha$ increases the probability density
for the $x$s concentrates just above $x=1$.

With heavy-tailed distributions, it can be difficult to predict future
observations from past ones, for two reasons. First, the observations may not
provide much information about the parameters (in this case, $\alpha$), and
second, even conditional on the parameters, the predictive distribution for
future data can be heavy-tailed, implying a lot of uncertainty.

\section{Computational cost}
